---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Ari Roberson"
date: "8/29/2019"
output: 
  html_document: 
    fig_height: 7
    fig_width: 10
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

### Exercise 1

The datasaurus_dozen file has 1846 rows and 3 columns (the number of variables represents the number of columns). The variables are "dataset", "x", and "y" .

### Exercise 2

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
This r value indicates that `x` and `y` have an extremely weak, negative linear relationship. It is not capable of telling us exactly how `x` and `y` ARE related, such as, that they create the image of a dino.

### Exercise 3

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The datasuarus_dozen data frame is now being filtered for observations where the data is related to star. The following code plots the star created by the star_data data set.

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

The correlation coefficient is very similar to the dino. They are both about -0.06 yet have very different visuals. Because they are shapes rather than functions, the correlation coefficient does not provide much information about the data set.

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r}
circle_data %>%
  summarize(r = cor(x, y))
```

Filtering the data frame to only use data with name "circle" allows the circle to be used. The next plot of code plots the circle with the filtered data. The r value for the circle is also -0.06 even with the difference in physical appearance.

### Exercise 5

```{r}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~ dataset, ncol = 5) +
  theme(legend.position = "left")
```

The `color = data` made each of the datasets a different color, the one they were each set to be. The `ncol = 3` organized the plots into 3 columns. Changing this number would alter the number of columns in which the plots appear. The `facet_wrap()`split the plot into multiple plots so each of the data sets could be seen individually. The `theme(legend.position = "none")` positions the legend for the plots if there was one. The term `none` makes the legend not appear at all. However, it could go at the `top`, `bottom`, `left`, or `right`.

```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x,y)) %>%
  print(13)
```

This section of code calculates each r value according to dataset and lists all of them. Each of the correlation coefficients are between -0.07 and -0.06 yet look almost nothing alike, showing that r does not give any information about the picutre of the plots except that they have close to no linear relationship.

